Paper notes

### 2019-08-15 paper_notes.Rmd
OK formula

f_eth <- function(i_e,M,x,n,S){
  if (x > n){
    U <- NA}else{
  if (x < round(n*i_e,digits = 2)){
   U <- (x / round((n*i_e),digits = 2)) * S
    }else if (x > round((n*i_e),digits = 2)){
      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
    }else{
        U <- 1}
  round(U,digits = 2)
    }
}

@@

@@

$$
U_e=
\begin{cases}
1, & \text{if} \ x = n\times i_e, \\
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
M + ((1 - \frac{x}{n}) \times (1 - M)) / (1 - i_e), & \text{if} \ x > n\times i_e 
\end{cases}
$$

@@

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 1

@@

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = "desired distance = 0.2") + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

@@

i_e = 0.5
M = 0
S = 1
n = 7

@@

i_v <- 0.2
S  <- 0
M <- 1

>>>>

 f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
   if (x < round(n*i_e,digits = 2)){
    U <- (x / round((n*i_e),digits = 2)) * S
     }else {
       U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
     }
   round(U,digits = 2)
     }
 }

@@

# f_val <- function(e_w,ew_ng,M,i_v,S){
#   if (round(abs(e_w-ew_ng), digits=2) < i_v) {
#     U <- 1
#     }else{
#       U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
#     }
#   round(U,digits = 2)
# }

@@

$$
U_e=
\begin{cases}
(\frac{x}{n \times i_e})\times S, & \text{if} \ x < n\times i_e, \\
M + \frac{(1 - \frac{x}{n}) \times (1 - M)}{1 - i_e}, & \text{if} \ x \geq n\times i_e 
\end{cases}
$$

@@

$$
U_v=
\begin{cases}
1, & \text{if} \ e_w \leq i_v, \\
\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S, & otherwise
\end{cases}
$$

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S <- 0
M <- 0 #M can be either 0 or 1, M = 0 is for declining slope, M = 1 keeps utility = 1 for values out of range, so S = 0 keeps  the threshold  with values out of the distance equal 0

@@

subt_cont <- paste0("desired distance = ",i_v)

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Symmetric Single Peaked \n\r (S=1,M=0) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

thres_val_plot <- thres_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "utility for location") + ggtitle(label = "Threshold Schelling \n\r (S=0,M=1) ",subtitle = subt_cont) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1))

@@

i_e = 0.7
M = 1
S = 0
n = 8

@@

i_v <- 0.1
S  <- 1
M <- 0 #different values  of M do change results, even for M < 1
